### 2020-12-18 ch02_scientific_background/scientific_background.tex
Finished chapter 2 and solved formatting issues with underfull vboxes

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/tcr_calculation.pdf}
  \caption{Global and annual mean near-surface air temperature change $\Delta
    T$ for 140 years of a simulation with a \pct{1} per year increase of the
    atmospheric \ac{CO2} concentration (\onepctcotwo{}) for the \acf{CESM} of
    the \acf{NCAR} (blue circles). The temperature change is calculated
    relative to a corresponding pre-industrial control simulation smoothed
    with a linear fit over all 140 years. The \acf{TCR} is defined as $\Delta
    T$ at the time of \acs{CO2} doubling averaged over a 20 year period
    (illustrated by the vertical dashed lines). Here, $\text{TCR} = 2.35
    \unit{K}$ (horizontal dashed line).}
  \label{fig:02:tcr}
\end{figure}

@@

linear emergent relationship for the climate model ensemble $\left\{ \left(
x_m, y_m \right) \right\}$, a linear regression model

@@

  P(y|x) = \frac{1}{\sqrt{2 \pi \sigma_{\hat{y}}^2(x)}} \exp \left[

@@

  P(x_0|x) = \frac{1}{\sqrt{2 \pi \sigma_x^2}} \exp \left[ -\frac{\left( x_0 -
    x \right)^2}{2 \sigma_x^2} \right],

@@

$-\infty$ and $+\infty$ and using Bayes' theorem implies $P(x_0|x) = P(x|x_0)$.
In a final step, this can be used to calculate the posterior \ac{PDF} for the
constrained prediction of the target variable $y$ given the observation $x_0$
(gray \ac{PDF} in \cref{fig:02:emergent_constraint}) with numerical
integration:

@@

  P(y|x_0) = \int_{-\infty}^{+\infty} P(y|x) \, P(x|x_0) \dd{}x.

@@

One limitation of the presented approach is the assumption that the individual
data points from the different climate models are independent. As already noted
in the beginning of \cref{sec:02:reducing_uncertainties}, this is not the case
for typical climate models ensembles, as some modeling groups provide output
for multiple climate models and some climate models from different modeling
institutions share components and code \autocite{Knutti2013}. The duplicated
code in the different climate models leads to an overestimation of the sample
size and may result in spurious correlations \autocite{Sanderson2015}. Possible
approaches to tackle this problem are presented in
\cref{subsec:02:model_weighting} and include a weighting of the climate models
based on their degree of interdependence \autocite{Knutti2017a, Sanderson2015,
  Sanderson2017}. A further limitation of this approach is the use of an
ordinary least squares linear regression model. This is not always appropriate,
for example when a non-linear emergent relationship is expected
\autocite{Nijsse2020} or when additional physical considerations further
constrain the regression model, \eg{} by demanding a zero intercept ($\hat{b}_0
= 0$) \autocite{Annan2020, JimenezdelaCuesta2019}. Moreover, using only a
single observational dataset to estimate $x_0$ and $\sigma_x$ when different
datasets are available might lead to an underestimation of the observational
uncertainty, as different observational datasets might lead to different
emergent constraints.

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/tcr_calculation.pdf}
  \caption{Global and annual mean near-surface air temperature change $\Delta
    T$ for 140 years of a simulation with a \pct{1} per year increase of the
    atmospheric \ac{CO2} concentration (\onepctcotwo{}) for the \acf{CESM} of
    the \acf{NCAR} (blue circles). The temperature change is calculated
    relative to a corresponding pre-industrial control simulation smoothed
    with a linear fit over all 140 years. The \acf{TCR} is defined as the
    temperature change $\Delta T$ at the time of \acs{CO2} doubling averaged
    over a 20 year period (illustrated by the vertical dashed lines). Here,
    $\text{TCR} = 2.35 \unit{K}$ (horizontal dashed line).}
  \label{fig:02:tcr}
\end{figure}

@@

linear emergent relationship for a climate model ensemble with $M$ climate
models and data $\left\{ \left( x_m, y_m \right) \mid m \in I_M \right\}$ with index set $I_M = \left\{ 1, 2, \ldots, M\right\}$, a linear
regression model

@@

  \cond{y}{x} = \frac{1}{\sqrt{2 \pi \sigma_{\hat{y}}^2(x)}} \exp \left[

@@

  \cond{x_0}{x} = \frac{1}{\sqrt{2 \pi \sigma_x^2}} \exp \left[ -\frac{\left(
    x_0 - x \right)^2}{2 \sigma_x^2} \right],

@@

$-\infty$ and $+\infty$ and using Bayes' theorem implies $\cond{x_0}{x} =
\cond{x}{x_0}$. In a final step, this can be used to calculate the posterior
\ac{PDF} for the constrained prediction of the target variable $y$ given the
observation $x_0$ (gray \ac{PDF} in \cref{fig:02:emergent_constraint}) with
numerical integration:

@@

  \cond{y}{x_0} = \int_{-\infty}^{+\infty} \cond{y}{x} \, \cond{x}{x_0} \dd{}x.

@@

A convenient metric to quantify the skill of an emergent relationship is the
coefficient of determination $R^2$ of its underlying statistical model. In the
presented framework which is based on univariate ordinary least squares
regression, $R^2$ is given by the squared Pearson correlation coefficient $r$
evaluated on the climate model ensemble data $\left\{ \left( x_m, y_m \right)
\mid m \in I_M \right\}$, \ie{} $R^2 = r^2$. A further quantity describing the
skill of an emergent relationship is its statistical significance. In the
introduced framework, a two-sided $t$-test can be used to determine how likely
the correlation found between the target variable $y$ and the predictor $x$
would be to appear by chance. The null hypothesis for this test is that the
predictor and the target variable are not linearly correlated, \ie{} that the
true underlying Pearson correlation coefficient of the population is zero. If
this null hypothesis is true, the probability distribution of the variable
\begin{equation}
  t = \frac{r \sqrt{M - 2}}{\sqrt{1 - r^2}}
  \label{eq:02:t}
\end{equation}
is a Student's $t$-distribution with $M - 2$ degrees of freedom. The
statistical significance can then be measured with the $p$-value of this
two-sided $t$-test, which describes the probability of obtaining an absolute
sample Pearson correlation coefficient greater than $\abs*{r}$ if the null
hypothesis is true. Smaller $p$-values indicate higher a higher statistical
significance and vice versa.

One limitation of the presented framework is the assumption that the individual
data points from the different climate models are independent. As already noted
in the beginning of \cref{sec:02:reducing_uncertainties}, this is not the case
for typical climate models ensembles, as some modeling groups provide output
for multiple climate models and some climate models from different modeling
institutions share components and code \autocite{Knutti2013}. The duplicated
code in the different climate models leads to an overestimation of the sample
size and may result in spurious correlations \autocite{Sanderson2015}. Possible
approaches to tackle this problem are presented in
\cref{subsec:02:model_weighting} and include a weighting of the climate models
based on their degree of interdependence \autocite{Knutti2017a, Sanderson2015,
  Sanderson2017}. A further limitation of this approach is the use of an
ordinary least squares linear regression model. This is not always appropriate,
for example when a non-linear emergent relationship is expected
\autocite{Nijsse2020} or when additional physical considerations further
constrain the regression model, \eg{} by demanding a zero intercept ($\hat{b}_0
= 0$) \autocite{Annan2020, JimenezdelaCuesta2019}. Moreover, using only a
single observational dataset to estimate $x_0$ and $\sigma_x$ when different
datasets are available might lead to an underestimation of the observational
uncertainty, as different observational datasets might lead to different
emergent constraints.
